Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells

### 2019-05-16 Paper/paper.tex

Some energetic and geometric parameters were also obtained from clusters and molecules in the gas phase using the ADF package.
Here, for consistency with other parameters obtained previously for ReaxFF, the B3LYP functional has been used with TZP STO--basis functions.
Scalar relativistic effects were introduced using the ZORA correction.

>>>>

Differences in energies and optimized geometries were also obtained from clusters in the gas phase using \emph{Gaussian16} \textbf{put references}.
For these calculations, the B3LYP functional has been used with the aug--cc--pVTZ basis functions for oxygen and for lanthanum the La basis set from the Stuttgart/Dresden group, La(RSC97) \textbf{double check} with a 28--electron ECP \textbf{citation}.
By using this approach, we ensure that the parameters obtained for lanthanum in these calculations are consistent with the way the oxygen parameters were obtained in previous studies.
